### 2018-06-27 README.Rmd
update readme

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# An evaluation framework for trajectory inference methods

![travis](https://travis-ci.com/Zouter/dynalysis.svg?token=pzNqJjk3yapU1Hk7sDg8&branch=master)

### Installation

You can install dynalysis from github with:

```{r gh-installation, eval = FALSE}
install.packages("devtools")
setRepositories(ind = 1:2)
devtools::install_github("Zouter/dynalysis", dependencies = T, upgrade = T)
```

### Running

To run locally, install `docker` and run `docker build -t dynalysis .`

### Licenses

**Text and figures:**  [CC-BY-4.0](http://creativecommons.org/licenses/by/4.0/)

**Code:** See the [DESCRIPTION](DESCRIPTION) file

$\textbf{Data:}$ [CC-0](http://creativecommons.org/publicdomain/zero/1.0/) attribution requested in reuse

### Contributions

We welcome contributions from everyone. Before you get started, please see our [contributor guidelines](CONTRIBUTING.md). Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.

>>>>

# dynbenchmark

[![Build Status](https://api.travis-ci.org/dynverse/dynbenchmark.svg)](https://travis-ci.org/dynverse/dynbenchmark)
![Lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)

Scripts to reproduce the manuscript

A comparison of single-cell trajectory inference methods: towards more accurate and robust tools  
Wouter Saelens\*, Robrecht Cannoodt\*, Helena Todorov, Yvan Saeys  
bioRxiv 276907; doi: https://doi.org/10.1101/276907

## Datasets

We include the following datasets. When using any of these datasets, please also cite our preprint: [![DOI](https://zenodo.org/badge/DOI/10.1101/276907.svg)](https://doi.org/10.1101/276907)

* [![DOI](https://zenodo.org/badge/DOI/10.5281/zenodo.1211533.svg)](https://doi.org/10.5281/zenodo.1211533) Single-cell -omics datasets, both real and synthetic, used to evaluated the trajectory inference methods
* **Coming soon** Main results of the evaluation, used to rank the methods and construct practical guidelines
